---
title: "ThesisAnalysis"
author: "Kassia Orychock"
date: '2019-01-31'
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r, echo = FALSE, warning = FALSE}
options(scipen = 2, digits = 4)
library(knitr)
opts_chunk$set(warning = FALSE)
```

This Rmd file will be used as the file for my Thesis Analysis on causal mediation.

# Libraries
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(car)
library(foreign)
library(Hmisc)
library(survival)
library(tableone)
```

# Reading of Raw Survey Data
```{r}
ibiccs_readin <- read.csv("Database_recoded_2012-2014_weights_Walkscore_RTA.csv")
ibiccs_readin$TransitScore <- as.numeric(ibiccs_readin$TransitScore)
ibiccs_readin$BikeScore <- as.numeric(ibiccs_readin$BikeScore)
```

# Filtering Out Cities
```{r}
Boston <- filter(ibiccs_readin, ville == "Boston")

Chicago <- filter(ibiccs_readin, ville == "Chicago")

Detroit <- filter(ibiccs_readin, ville == "Détroit")

NewYork <- filter(ibiccs_readin, ville == "New-York")

Philadelphia <- filter(ibiccs_readin, ville == "Philadelphie")

Montreal <- filter(ibiccs_readin, ville == "Montréal")

Toronto <- filter(ibiccs_readin, ville == "Toronto")

Vancouver <- filter(ibiccs_readin, ville == "Vancouver")
```

# Filtering Out Variables in USA Data
```{r}
ibiccs <- select(ibiccs_readin, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Boston1 <- select(Boston, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Chicago1 <- select(Chicago, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Detroit1 <- select(Detroit, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

NewYork1 <- select(NewYork, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Philadelphia1 <- select(Philadelphia, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Montreal1 <- select(Montreal, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Toronto1 <- select(Toronto, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Vancouver1 <- select(Vancouver, lang, q54, ville, q1us, q46b7, q2, q13, q14, q15, q16, q17, q18, q19, q20, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q24, q25, q26, q27, q28, q40, q41, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

city <- rbind(Philadelphia1, NewYork1, Detroit1, Chicago1, Boston1, Montreal1, Toronto1, Vancouver1)
```

# Binding by Country
```{r}
city_USA <- rbind(Philadelphia1, NewYork1, Detroit1, Chicago1, Boston1)
city_CAN <- rbind(Montreal1, Toronto1, Vancouver1)
```


# Descriptive Stats for Each City
```{r, echo = FALSE, warning = FALSE}
describe(Boston1)
describe(Chicago1)
describe(Detroit1)
describe(NewYork1)
describe(Philadelphia1)
describe(Montreal1)
describe(Toronto1)
describe(Vancouver1)
```


# Descriptive Stats for Merged Cities
```{r, echo = FALSE, warning = FALSE}
Hmisc::describe(city)
```


#Tables for Each City and Combined
```{r}
vars <- c('lang', 'q54', 'ville', 'q1us', 'q46b7', 'q2', 'q13', 'q14', 'q15', 'q16', 'q17', 'q18', 'q19', 'q20', 'q21', 'q22b', 'q22c', 'q22d', 'q22e', 'q22f_m1', 'q23', 'q24', 'q25', 'q26', 'q27', 'q28', 'q40', 'q41', 'q42', 'q44', 'q45', 'q46b', 'q47', 'q48', 'q49', 'q50', 'q51', 'Q52_occupational_status_category', 'q53', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')
CreateTableOne(vars = vars, data = Boston1)
CreateTableOne(vars = vars, data = Chicago1)
CreateTableOne(vars = vars, data = Detroit1)
CreateTableOne(vars = vars, data = NewYork1)
CreateTableOne(vars = vars, data = Philadelphia1)
CreateTableOne(vars = vars, data = Montreal1)
CreateTableOne(vars = vars, data = Toronto1)
CreateTableOne(vars = vars, data = Vancouver1)
CreateTableOne(vars = vars, data = city)

tab1 <- ibiccs %>%
          group_by(ville)
```

# Fix this Code - Breaks Session
table1 <- ibiccs %>%
            group_by(ville) %>%
              CreateTableOne(vars = vars, data = ibiccs)


lang_lm <- lm(bmi ~ cbind(lang, q2), Boston1)
tidy(lang_lm)

# Histogram of BMI
```{r}
hist_bmi <- ggplot(city, aes(bmi)) + 
  geom_histogram()
plot(hist_bmi)

hist_bmi_Boston <- ggplot(Boston1, aes(bmi)) + 
  geom_histogram()
plot(hist_bmi)
```


## Junk Code
```
lm1 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + TransitScore + GroceryScore + factor(ville), data = ibiccs)
summary(lm1)
confint(lm1)

lm2 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + + TransitScore + GroceryScore + factor(ville) + lang + q44 + q47 + q51 + Q52_occupational_status_category + q54, data = ibiccs)
summary(lm2)
confint(lm2)
```


```
lm3 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + TransitScore + GroceryScore + factor(ville), data = city_CAN)
summary(lm3)
confint(lm3)

lm4 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + + TransitScore + GroceryScore + factor(ville) + lang + q44 + q47 + q51 + Q52_occupational_status_category + q54, data = city_CAN)
summary(lm4)
confint(lm4)

lm5 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + TransitScore + GroceryScore + factor(ville), data = city_USA)
summary(lm1)
confint(lm1)


lm6 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + + TransitScore + GroceryScore + factor(ville) + lang + q44 + q47 + q51 + Q52_occupational_status_category + q54, data = city_USA)
summary(lm2)
confint(lm2)
```

```
usda_zip <- dplyr::full_join(USDA, USA_ZIP, by = "CensusTract")

usda_zip_food <- usda_zip %>%
                    group_by(zip) %>%
                        summarize(
                          food = mean(foodvariable)
                        )
```

## Rename Variables
```
library(plyr)
city$zip <- as.numeric(city$RTA_zip)
USA_ZIP$CensusTract <- as.numeric(USA_ZIP$tract)
```

```
library(plyr)
city$CensusTract <- as.numeric(city$zip)
```


```
city_zip <- dplyr::left_join(city, usda_zip, by = "zip")
table(city_zip$ville)

summary(city$WalkScore)
summary(city$DiningandDrinkingScore)
summary(city$GroceryScore)
summary(city$TransitScore)
```

