---
title: "ThesisAnalysis"
author: "Kassia Orychock"
date: '2019-01-31'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE}
options(scipen = 2, digits = 4)
library(knitr)
opts_chunk$set(warning = FALSE)
```

This Rmd file will be used as the file for my Thesis Analysis on causal mediation.

# Libraries
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(car)
library(foreign)
library(Hmisc)
library(knitr)
library(dplyr)
library(survival)
library(finalfit)
library(tableone)
library(lme4)
library(e1071)
library(mediation)
```

# Reading of Raw Survey Data
```{r}
ibiccs_readin <- read.csv("Database_recoded_2012-2014_weights_Walkscore_RTA.csv")
ibiccs_readin$TransitScore <- as.numeric(ibiccs_readin$TransitScore)
ibiccs_readin$BikeScore <- as.numeric(ibiccs_readin$BikeScore)
```

# Recode BMI
```{r}
## BMI
ibiccs_clean <- ibiccs_readin %>%
	mutate(bmi_category = case_when(
		bmi < 18.5 ~ "underweight",
		bmi >=30 & bmi <999 ~ "obese",
		bmi >=25 & bmi <30 ~ "overweight",
		bmi >=18.5 & bmi <25 ~ "normal weight",
		bmi == 9999 ~ "NA",
		TRUE ~ "other"
	))

table(ibiccs_clean$bmi, ibiccs_clean$bmi_category)

summary(ibiccs_clean$bmi)
```

# Recode Language
```{r}
table(ibiccs_clean$lang)
## Language
ibiccs_clean <- ibiccs_clean %>%
	mutate(language = case_when(
		lang == "Anglais" ~ "English",
		lang == "Espagnol" ~ "Fren/Span",
		lang == "Français" ~ "Fren/Span"
	))
table(ibiccs_clean$lang, ibiccs_clean$language)
```

# Recode Gender
```{r}
table(ibiccs_clean$q54)
#Gender
ibiccs_clean <- ibiccs_clean %>%
  mutate(gender = case_when(
    q54 == "Femme" ~ "Female",
    q54 == "Homme" ~ "Male"
  ))
table(ibiccs_clean$q54, ibiccs_clean$gender)
```

# Recode Self-Rated Health
```{r}
table(ibiccs_clean$q2)
ibiccs_clean <- ibiccs_clean %>%
  mutate(health = case_when(
    q2 == "Excellent" ~ "Excellent",
    q2 == "Très bon" ~ "Very Good",
    q2 == "Bon" ~ "Good",
    q2 == "Moyen" ~ "Poor/Fair",
    q2 == "Mauvais" ~ "Poor/Fair"
  ))
table(ibiccs_clean$q2, ibiccs_clean$health)
```

# Recode Transportation
```{r}
table(ibiccs_clean$q13)
ibiccs_clean <- ibiccs_clean %>%
  mutate(common_transportation = case_when(
    q13 == "Marche" ~ "Walking",
    q13 == "Véhicule motorisé (loué, emprunté, covoiturage)" ~ "Car",
    q13 == "Voiture personnelle" ~ "Car",
    q13 == "Scooter" ~ "Other",
    q13 == "Taxi" ~ "Other",
    q13 == "Autre (précisez:)" ~ "Other",
    q13 == "Transport en commun" ~ "Public Transportation",
    q13 == "Vélo en libre-service" ~ "Bicycle",
    q13 == "Vélo personnel" ~ "Bicycle"
  ))
table(ibiccs_clean$q13, ibiccs_clean$common_transportation)
```

# Recode Physically Active (Y/N)
```{r}
table(ibiccs_clean$q14)
ibiccs_clean <- ibiccs_clean %>%
  mutate(physically_active = case_when(
    q14 == "Oui" ~ "Yes",
    q14 == "Non" ~ "No"
  ))
table(ibiccs_clean$q14, ibiccs_clean$physically_active)
```

# Recode Type of Physical Activity 
```{r}
# Code into Sedentary, Walking, Moderate, Vigorous Activity
table(ibiccs_clean$q18)
  ibiccs_clean <- ibiccs_clean %>%
    mutate(pa_level = case_when(
      q15 == 1 ~ "Low",
      q15 == 2 ~ "Moderate",
      q15 == 3 ~ "Low",
      q15 == 4 ~ "Moderate",
      q15 == 5 ~ "Vigorous",
      q15 == 6 ~ "Moderate",
      q15 == 7 ~ "Moderate",
      q15 == 8 ~ "Low",
      q15 == 9 ~ "Low",
      q15 == 10 ~ "Vigorous",
      q15 == 11 ~ "Vigorous",
      q15 == 12 ~ "Moderate",
      q15 == 13 ~ "Low",
      q15 == 14 ~ "Vigorous",
      q15 == 15 ~ "Vigorous",
      q15 == 16 ~ "Sedentary",
      q15 == 17 ~ "Low",
      q15 == 18 ~ "Moderate",
      q15 == 19 ~ "Low",
      q15 == 20 ~ "Moderate",
      q15 == 21 ~ "Moderate",
      q15 == 22 ~ "Vigorous",
      q15 == 23 ~ "Vigorous",
      q15 == 24 ~ "Low",
      q15 == 25 ~ "Low",
      q15 == 26 ~ "Low",
      q15 == 27 ~ "Moderate",
      q15 == 28 ~ "Vigorous",
      q15 == 29 ~ "Vigorous",
      q15 == 30 ~ "Vigorous",
      q15 == 31 ~ "Low",
      q15 == 32 ~ "Moderate",
      q15 == 33 ~ "Moderate",
      q15 == 34 ~ "Moderate",
      q15 == 35 ~ "Moderate",
      q15 == 36 ~ "Moderate",
      q15 == 37 ~ "Vigorous",
      q15 == 38 ~ "Vigorous",
      q15 == 39 ~ "Vigorous",
      q15 == 40 ~ "Vigorous",
      q15 == 41 ~ "Vigorous",
      q15 == 42 ~ "Moderate",
      q15 == 43 ~ "Moderate",
      q15 == 44 ~ "Vigorous",
      q15 == 45 ~ "Low",
      q15 == 46 ~ "Moderate",
      q15 == 47 ~ "Moderate",
      q15 == 48 ~ "Vigorous",
      q15 == 49 ~ "Moderate",
      q15 == 50 ~ "Moderate",
      q15 == 51 ~ "Vigorous",
      q15 == 52 ~ "Vigorous",
      q15 == 53 ~ "Vigorous",
      q15 == 54 ~ "Moderate",
      q15 == 55 ~ "Low",
      q15 == 56 ~ "Vigorous",
      q15 == 57 ~ "Moderate",
      q15 == 58 ~ "Vigorous",
      q15 == 59 ~ "Moderate",
      q15 == 60 ~ "Vigorous",
      q15 == 61 ~ "Vigorous",
      q15 == 62 ~ "Vigorous",
      q15 == 63 ~ "Vigorous",
      q15 == 64 ~ "Moderate",
      q15 == 65 ~ "Moderate",
      q15 == 66 ~ "Vigorous",
      q15 == 67 ~ "Vigorous",
      q15 == 68 ~ "Low",
      q15 == 69 ~ "Moderate",
      q15 == 96 ~ "NA",
      q15 == 97 ~ "Sedentary",
      q15 == 98 ~ "NA",
      q15 == 99 ~ "NA",
      TRUE ~ "NA"
    ))
table(ibiccs_clean$q15, ibiccs_clean$pa_level)
```

# Recode Days Per Week Spent Travelling via Car
```{r}
table(ibiccs_clean$q21)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_motor_vehicle = case_when(
    q21 == 0 ~ 0,
    q21 == 1 ~ 1,
    q21 == 2 ~ 2,
    q21 == 3 ~ 3,
    q21 == 4 ~ 4,
    q21 == 5 ~ 5,
    q21 == 6 ~ 6,
    q21 == 7 ~ 7,
    q21 == 98 ~ NA_real_,
    q21 == 99 ~ NA_real_
  ))
table(ibiccs_clean$day_per_week_motor_vehicle)
```

# Recode Days Per Week Spent Travelling via Public Transport
```{r}

table(ibiccs_clean$q23)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_public_transit = case_when(
    q23 == 0 ~ 0,
    q23 == 1 ~ 1,
    q23 == 2 ~ 2,
    q23 == 3 ~ 3,
    q23 == 4 ~ 4,
    q23 == 5 ~ 5,
    q23 == 6 ~ 6,
    q23 == 7 ~ 7,
    q23 == 8 ~ NA_real_,
    q23 == 9 ~ NA_real_
  ))

table(ibiccs_clean$q23, ibiccs_clean$day_per_week_public_transit)
```

# Recode Days Per Week Spent Travelling via Walking
```{r}

table(ibiccs_clean$q25)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_walking = case_when(
    q25 == 0 ~ 0,
    q25 == 1 ~ 1,
    q25 == 2 ~ 2,
    q25 == 3 ~ 3,
    q25 == 4 ~ 4,
    q25 == 5 ~ 5,
    q25 == 6 ~ 6,
    q25 == 7 ~ 7,
    q25 == 8 ~ NA_real_,
    q25 == 9 ~ NA_real_
  ))

table(ibiccs_clean$q25, ibiccs_clean$day_per_week_walking)
```

# Recode Days Per Week Spent Travelling via Bike
```{r}

table(ibiccs_clean$q27)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_bike = case_when(
    q27 == 0 ~ 0,
    q27 == 1 ~ 1,
    q27 == 2 ~ 2,
    q27 == 3 ~ 3,
    q27 == 4 ~ 4,
    q27 == 5 ~ 5,
    q27 == 6 ~ 6,
    q27 == 7 ~ 7,
    q27 == 98 ~ NA_real_,
    q27 == 99 ~ NA_real_
  ))

table(ibiccs_clean$q27, ibiccs_clean$day_per_week_bike)
```

# Recode Age
```{r}
summary(ibiccs_clean$q42)
#CCHS/STATCAN or continuous
```

# Recode Marital Status
```{r}
table(ibiccs_clean$q44)
ibiccs_clean <- ibiccs_clean %>%
  mutate(marital_status = case_when(
    q44 == "Célibatiare" ~ "Single",
    q44 == "Divorcé(e)" ~ "Divorced/Separated/Widowed",
    q44 == "En couple" ~ "Relationship/Married/Common-Law",
    q44 == "Marié(e)/Conjoint de fait" ~ "Relationship/Married/Common-Law",
    q44 == "Séparé(e)" ~ "Divorced/Separated/Widowed",
    q44 == "Veuf(ve)" ~ "Divorced/Separated/Widowed"
  ))
table(ibiccs_clean$q44, ibiccs_clean$marital_status)
```

# Recode Number of Children in Home
```{r}
table(ibiccs_clean$q45)
ibiccs_clean <- ibiccs_clean %>%
  mutate(children_household = case_when(
    q45 == 1 ~ 1,
    q45 == 2 ~ 2,
    q45 == 3 ~ 3,
    q45 == 4 ~ 3,
    q45 == 5 ~ 3,
    q45 == 6 ~ 3,
    q45 == 7 ~ 3,
    q45 == 8 ~ 0,
    q45 == 9 ~ NA_real_
  ))
table(ibiccs_clean$q45, ibiccs_clean$children_household)
```

# Recode Months in Current Home?
```{r}
summary(ibiccs_clean$q46b)
```

# Recode Ethnicity
```{r}
table(ibiccs_clean$q47)
ibiccs_clean <- ibiccs_clean %>%
  mutate(ethnicity = case_when(
    q47 == "Amérindien des États-Unis / Autochtone d'Amérique" ~ "Native American/Indigenous",
    q47 == "Arabe (Moyen-Orient, Afrique du Nord)" ~ "Other",
    q47 == "Asiatique / insulaire du Pacifique" ~ "Asian",
    q47 == "Autre" ~ "Other",
    q47 == "Blanc(che) / Caucasien" ~ "Caucasian",
    q47 == "Hispanique / Latino / Espagnol(e)" ~ "Hispanic",
    q47 == "Indien / Pakistanais" ~ "Other",
    q47 == "Jewish" ~ "Other",
    q47 == "Mixed / Mixed race / Bi-racial" ~ "Other",
    q47 == "Noir(e) / Africain(e) / Afro-Américain(e)" ~ "African American/Canadian"
  ))
table(ibiccs_clean$q47, ibiccs_clean$ethnicity)
```

# Recode Country Born
```{r}
table(ibiccs_clean$q48)
ibiccs_clean <- ibiccs_clean %>%
  mutate(country_born = case_when(
    q48 == 1 ~ "Canada",
    q48 == 2 ~ "United States",
    q48 >= 3 ~ "Other", 
    q48 <= 81 ~ "Other",
    q48 == 96 ~ "Other"
  ))
table(ibiccs_clean$q48, ibiccs_clean$country_born)
```

# Recode Motor Vehicle Access
```{r}
table(ibiccs_clean$q50)

ibiccs_clean <- ibiccs_clean %>%
  mutate(motor_vehicle_access = case_when(
    q50 == "Non" ~ "No",
    q50 == "Oui" ~ "Yes"
  ))
table(ibiccs_clean$q50, ibiccs_clean$motor_vehicle_access)
```

# Recode Education Level
```{r}
table(ibiccs_clean$q51)
ibiccs_clean <- ibiccs_clean %>%
  mutate(education = case_when(
    q51 == "Aucun grade, certificat ou diplôme" ~ "High School/Lower",
    q51 == "Baccalauréat" ~ "Baccalaureate",
    q51 == "Cégep" ~ "Cégep",
    q51 == "Certificat d'école de métier, certificat ou diplôme" ~ "Certificate/Diploma",
    q51 == "Diplôme d'études secondaire ou l'équivalent" ~ "High School/Lower",
    q51 == "Diplôme universitaire supérieur au baccalauréat" ~ "Graduate School",
    q51 == "École primaire" ~ "High School/Lower"
  ))
table(ibiccs_clean$q51, ibiccs_clean$education)
```

# Recode Occupation Status
```{r}
table(ibiccs_clean$Q52_occupational_status_category)
ibiccs_clean <- ibiccs_clean %>%
  mutate(occupation_status = case_when(
    Q52_occupational_status_category == "Disability" ~ "Unemployed",
    Q52_occupational_status_category == "Full time or Self-employed" ~ "Employed",
    Q52_occupational_status_category == "Homemaker or parental leave" ~ "Unemployed",
    Q52_occupational_status_category == "Part time" ~ "Employed",
    Q52_occupational_status_category == "Retired" ~ "Unemployed",
    Q52_occupational_status_category == "Student" ~ "Student",
    Q52_occupational_status_category == "Unemployed seeking work" ~ "Unemployed"
  ))
table(ibiccs_clean$Q52_occupational_status_category, ibiccs_clean$occupation_status)
```

# Recode Household Income
```{r}
table(ibiccs_clean$q53)
ibiccs_clean <- ibiccs_clean %>%
  mutate(household_income = case_when(
    q53 == "Moins de 10000 $ par année" ~ "$0-$49999",
    q53 == "Entre 10000 $ and 19999 $ par année" ~ "$0-$49999",
    q53 == "Entre 20000 $ and 34999 $ par année" ~ "$0-$49999",
    q53 == "Entre 35000 $ and 49999 $ par année" ~ "$0-$49999",
    q53 == "Entre 50000 $ and 74999 $ par année" ~ "$50000-$99999",
    q53 == "Entre 75000 $ and 99999 $ par année" ~ "$50000-$99999",
    q53 == "Entre 100000 $ and 149999 $ par année" ~ "$100000-$149999",
    q53 == "Entre 150000 $ and 199999 $ par année" ~ "$150000+",
    q53 == "Plus de 200000 $ par année" ~ "$150000+",
    q53 == "Refuse de répondre" ~ "Missing"
  ))
table(ibiccs_clean$q53, ibiccs_clean$household_income)
```

# Filtering Out Cities
```{r}
Boston <- filter(ibiccs_clean, ville == "Boston")
Chicago <- filter(ibiccs_clean, ville == "Chicago")
Detroit <- filter(ibiccs_clean, ville == "Détroit")
NewYork <- filter(ibiccs_clean, ville == "New-York")
Philadelphia <- filter(ibiccs_clean, ville == "Philadelphie")
Montreal <- filter(ibiccs_clean, ville == "Montréal")
Toronto <- filter(ibiccs_clean, ville == "Toronto")
Vancouver <- filter(ibiccs_clean, ville == "Vancouver")
```

# Filtering Out Variables in Clean Data & Filtering Cities
```{r}
vars_clean <- c('language', 'ville', 'gender', 'health', 'common_transportation', 'physically_active', 'pa_level', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'q42', 'marital_status', 'children_household', 'ethnicity', 'country_born', 'motor_vehicle_access', 'education', 'occupation_status', 'household_income', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')

ibiccs <- dplyr::select(ibiccs_clean, vars_clean)
Boston <- dplyr::select(Boston, vars_clean)
Chicago <- dplyr::select(Chicago, vars_clean)
Detroit <- dplyr::select(Detroit, vars_clean)
NewYork <- dplyr::select(NewYork, vars_clean)
Philadelphia <- dplyr::select(Philadelphia, vars_clean)
Montreal <- dplyr::select(Montreal, vars_clean)
Toronto <- dplyr::select(Toronto, vars_clean)
Vancouver <- dplyr::select(Vancouver, vars_clean)
city <- rbind(Philadelphia, NewYork, Detroit, Chicago, Boston, Montreal, Toronto, Vancouver)
```

#Tables for Each City and Combined
```{r}
vars <- c('language', 'ville', 'gender', 'health', 'common_transportation', 'physically_active', 'pa_level', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'q42', 'marital_status', 'children_household', 'ethnicity', 'country_born', 'motor_vehicle_access', 'education', 'occupation_status', 'household_income', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')
CreateTableOne(vars = vars, strata = "ville", data = ibiccs)
```

# Table of Cities Combined
```{r}
vars <- c('language', 'ville', 'gender', 'health', 'common_transportation', 'physically_active', 'pa_level', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'q42', 'marital_status', 'children_household', 'ethnicity', 'country_born', 'motor_vehicle_access', 'education', 'occupation_status', 'household_income', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')
CreateTableOne(vars = vars, data = ibiccs)
```

# Histogram of BMI
```{r}
hist_bmi <- ggplot(city, aes(bmi)) + 
  geom_histogram()
plot(hist_bmi)

hist_bmi_city <- ggplot(city, aes(bmi)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_bmi_city)
```

# Histogram of WalkScore
```{r}
hist_walkscore <- ggplot(city, aes(WalkScore)) + 
  geom_histogram()
plot(hist_walkscore)

hist_walkscore_city <- ggplot(city, aes(WalkScore)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_walkscore_city)
```

# Histogram of TransitScore
```{r}
hist_trasnsitscore <- ggplot(city, aes(TransitScore)) + 
  geom_histogram()
plot(hist_trasnsitscore)

hist_trasnsitscore_city <- ggplot(city, aes(TransitScore)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_trasnsitscore_city)
```

# Histogram of GroceryScore
```{r}
hist_groceryscore <- ggplot(city, aes(GroceryScore)) + 
  geom_histogram()
plot(hist_groceryscore)

hist_groceryscore_city <- ggplot(city, aes(GroceryScore)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_groceryscore_city)
```

# Histogram of DiningAndDrinkingScore
```{r}
hist_diningdrinkingscore <- ggplot(city, aes(DiningandDrinkingScore)) + 
  geom_histogram()
plot(hist_diningdrinkingscore)

hist_diningdrinkingscore_city <- ggplot(city, aes(DiningandDrinkingScore)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_diningdrinkingscore_city)
```

# Linear Regression
```{r}
explanatory <- c('language', 'ville', 'gender', 'health', 'physically_active', 'q42', 'marital_status', 'country_born', 'motor_vehicle_access', 'occupation_status', 'bmi_category', 'WalkScore', 'TransitScore', 'BikeScore', 'DiningandDrinkingScore', 'GroceryScore', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'children_household')
dependent <- "bmi"
ibiccs %>%
  finalfit.lm(dependent, explanatory, na.rm = TRUE)

# Regressions for variables that won't run in explanatory
educ_reg <- lm(bmi ~ factor(education), data = ibiccs)
summary(educ_reg)
confint(educ_reg)

tran_reg <- lm(bmi ~ factor(common_transportation), data = ibiccs)
summary(tran_reg)
confint(tran_reg)

income_reg <- lm(bmi ~ factor(household_income), data = ibiccs)
summary(income_reg)
confint(income_reg)

ethn_reg <- lm(bmi ~ factor(ethnicity), data = ibiccs)
summary(ethn_reg)
confint(ethn_reg)

pa_lvl_reg <- lm(bmi ~ factor(pa_level), data = ibiccs)
summary(pa_lvl_reg)
confint(pa_lvl_reg)
```
Interpretation: What covariates are we keeping?
'language', 'ville', 'gender', 'health', 'physically_active', 'q42', 'marital_status', 'country_born', 'motor_vehicle_access', 'occupation_status', 'bmi_category', 'WalkScore', 'DiningandDrinkingScore', 'GroceryScore', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'children_household', 'education', 'common_transportation', 'household_income', 'ethnicity', 'pa_level'

# Linear Regression
```{r}
lm1 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + GroceryScore + factor(ville), data = ibiccs)
summary(lm1)
confint(lm1)

lm2 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + GroceryScore + factor(ville) + education + occupation_status + household_income, data = ibiccs)
summary(lm2)
confint(lm2)

lm3 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + GroceryScore + factor(ville) + education + occupation_status + household_income + language + gender + marital_status + ethnicity, data = ibiccs)
summary(lm3)
confint(lm3)
```

# Scatter Plots for BMI & Variables
```{r}
#BMI & WalkScore
ggplot(ibiccs, aes(x = bmi, y = WalkScore)) + 
  geom_point() + 
  facet_wrap(~ ville)
```

# Complete cases 
```{r}
ibiccs_cc <- ibiccs %>% 
              drop_na("bmi", "GroceryScore", "WalkScore", "DiningandDrinkingScore")
```
We remove missing data for all variables. We go from 23901 observations to 20922 observations. 

# Causal Mediation
# GroceryScore
```{r}
med.fit <- glm(GroceryScore ~ WalkScore, family = gaussian(link = "identity"), data = ibiccs_cc) 
summary(med.fit)

out.fit <- glm(bmi ~ WalkScore * GroceryScore, family = gaussian(link = "identity"), data = ibiccs_cc)
summary(out.fit)

med.out <- mediate(med.fit, out.fit, treat = "WalkScore", mediator = "GroceryScore", sims = 100) 
summary(med.out)
```

# Step 2: Add all covariates *Focus*
```{r}
med.fit <- glm(GroceryScore ~ WalkScore + ville + gender + health + physically_active + q42 + marital_status + day_per_week_motor_vehicle + day_per_week_public_transit + day_per_week_walking + day_per_week_bike + children_household + common_transportation + ethnicity + pa_level, family = gaussian(link = "identity"), data = ibiccs_cc) 
summary(med.fit)

out.fit <- glm(bmi ~ WalkScore * GroceryScore + ville + gender + health + physically_active + q42 + marital_status + day_per_week_motor_vehicle + day_per_week_public_transit + day_per_week_walking + day_per_week_bike + children_household + common_transportation + ethnicity + pa_level, family = gaussian(link = "identity"), data = ibiccs_cc)
summary(out.fit)

med.out <- mediate(med.fit, out.fit, treat = "WalkScore", mediator = "GroceryScore", sims = 100) 
summary(med.out)
```

## DiningandDrinkingScore
```{r}
med.fit <- glm(DiningandDrinkingScore ~ WalkScore, family = gaussian(link = "identity"), data = ibiccs_cc) 
summary(med.fit)

out.fit <- glm(bmi ~ WalkScore * DiningandDrinkingScore, family = gaussian(link = "identity"), data = ibiccs_cc)
summary(out.fit)

med.out <- mediate(med.fit, out.fit, treat = "WalkScore", mediator = "DiningandDrinkingScore", sims = 100) 
summary(med.out)
```

# Step 2: Add all covariates *Focus*
```{r}
med.fit <- glm(DiningandDrinkingScore ~ WalkScore + ville + gender + health + physically_active + q42 + marital_status + day_per_week_motor_vehicle + day_per_week_public_transit + day_per_week_walking + day_per_week_bike + children_household + common_transportation + ethnicity + pa_level, family = gaussian(link = "identity"), data = ibiccs_cc) 
summary(med.fit)

out.fit <- glm(bmi ~ WalkScore * DiningandDrinkingScore + ville + gender + health + physically_active + q42 + marital_status + day_per_week_motor_vehicle + day_per_week_public_transit + day_per_week_walking + day_per_week_bike + children_household + common_transportation + ethnicity + pa_level, family = gaussian(link = "identity"), data = ibiccs_cc)
summary(out.fit)

med.out <- mediate(med.fit, out.fit, treat = "WalkScore", mediator = "DiningandDrinkingScore", sims = 100) 
summary(med.out)
```


### List of next steps
- Add in the city level model with glmer and interpretation
- Income stratified model
    - Rerun the model for categories of income
    - Create a new dataframe with only one level of income
    
# Area-Level Analysis
med.fit <- lm(smorale ~ free + #area-covariates, data = school)

out.fit <- lmer(late ~ free + smorale + #area-covariates + #covariates + (1 | SCH_ID), data = student)
  
med.out <- mediate(med.fit, out.fit, treat = "free", mediator = "smorale", 
  + control.value = 3, treat.value = 4, sims = 100) 
summary(med.out)
```
