---
title: "ThesisAnalysis"
author: "Kassia Orychock"
date: '2019-01-31'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE}
options(scipen = 2, digits = 4)
library(knitr)
opts_chunk$set(warning = FALSE)
```

This Rmd file will be used as the file for my Thesis Analysis on causal mediation.

# Libraries
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(car)
library(foreign)
library(Hmisc)
library(survival)
library(tableone)
```

# Reading of Raw Survey Data
```{r}
ibiccs_readin <- read.csv("Database_recoded_2012-2014_weights_Walkscore_RTA.csv")
ibiccs_readin$TransitScore <- as.numeric(ibiccs_readin$TransitScore)
ibiccs_readin$BikeScore <- as.numeric(ibiccs_readin$BikeScore)
```

# Recode BMI
```{r}
## BMI
ibiccs_clean <- ibiccs_readin %>%
	mutate(bmi_category = case_when(
		bmi < 18.5 ~ "underweight",
		bmi >=30 & bmi <999 ~ "obese",
		bmi >=25 & bmi <30 ~ "overweight",
		bmi >=18.5 & bmi <25 ~ "normal weight",
		TRUE ~ "other"
	))
```
<<<<<<< HEAD

# Recode Language
```{r}
table(ibiccs_clean$lang)
## Language
ibiccs_clean <- ibiccs_clean %>%
	mutate(language = case_when(
		lang == "Anglais" ~ "English",
		lang == "Espagnol" ~ "Fren/Span",
		lang == "Français" ~ "Fren/Span"
	))
table(ibiccs_clean$lang, ibiccs_clean$language)
```

# Recode Gender
```{r}
table(ibiccs_clean$q54)
#Gender
ibiccs_clean <- ibiccs_clean %>%
  mutate(gender = case_when(
    q54 == "Femme" ~ "Female",
    q54 == "Homme" ~ "Male"
  ))
table(ibiccs_clean$q54, ibiccs_clean$gender)
```

# Recode Self-Rated Health
```{r}
table(ibiccs_clean$q2)
ibiccs_clean <- ibiccs_clean %>%
  mutate(health = case_when(
    q2 == "Excellent" ~ "Excellent",
    q2 == "Très bon" ~ "Excellent",
    q2 == "Bon" ~ "Good",
    q2 == "Moyen" ~ "Poor",
    q2 == "Mauvais" ~ "Poor",
    q2 == "Ne sais pas/Refuse de répondre" ~ "NA"
  ))
table(ibiccs_clean$q2, ibiccs_clean$health)
```
# Recode Transportation
```{r}
table(ibiccs_clean$q13)
ibiccs_clean <- ibiccs_clean %>%
  mutate(common_transportation = case_when(
    q13 == "Marche" ~ "Walking",
    q13 == "Véhicule motorisé (loué, emprunté, covoiturage)" ~ "Car",
    q13 == "Voiture personnelle" ~ "Car",
    q13 == " Ne s'applique pas" ~ "Other",
    q13 == "Ne sais pas" ~ "Other",
    q13 == "Scooter" ~ "Other",
    q13 == "Taxi" ~ "Other",
    q13 == "Transport en commun" ~ "Public Transportation",
    q13 == "Vélo en libre-service" ~ "Bicycle",
    q13 == "Vélo personnel" ~ "Bicycle"
  ))
table(ibiccs_clean$q13, ibiccs_clean$common_transportation)
```

# Recode Physically Active (Y/N)
```{r}
table(ibiccs_clean$q14)
ibiccs_clean <- ibiccs_clean %>%
  mutate(physically_active = case_when(
    q14 == "Ne sais pas/Ne s'applique pas" ~ "Other",
    q14 == "Refuse de répondre " ~ "Other",
    q14 == "Oui" ~ "Yes",
    q14 == "Non" ~ "No"
  ))
table(ibiccs_clean$q14, ibiccs_clean$physically_active)
=======

# Recode Language
```{r}

table(ibiccs_clean$lang)

## Language
ibiccs_clean <- ibiccs_clean %>%
	mutate(language = case_when(
		lang == "Anglais" ~ "English",
		lang == "Espagnol" ~ "Fren/Span",
		lang == "Français" ~ "Fren/Span"
	))

table(ibiccs_clean$lang, ibiccs_clean$language)
```

# Recode Gender
```{r}

table(ibiccs_clean$q54)

#Gender
ibiccs_clean <- ibiccs_clean %>%
  mutate(gender = case_when(
    q54 == "Femme" ~ "Female",
    q54 == "Homme" ~ "Male"
  ))

table(ibiccs_clean$q54, ibiccs_clean$gender)
```

# Recode Self-Rated Health
```{r}

table(ibiccs_clean$q2)

ibiccs_clean <- ibiccs_clean %>%
  mutate(health = case_when(
    q2 == "Excellent" ~ "Excellent",
    q2 == "Très bon" ~ "Excellent",
    q2 == "Bon" ~ "Good",
    q2 == "Moyen" ~ "Poor",
    q2 == "Mauvais" ~ "Poor",
    q2 == "Ne sais pas/Refuse de répondre" ~ "NA"
  ))

table(ibiccs_clean$q2, ibiccs_clean$health)
```

# Recode Transportation
```{r}

table(ibiccs_clean$q13)

ibiccs_clean <- ibiccs_clean %>%
  mutate(common_transportation = case_when(
    q13 == "Marche" ~ "Walking",
    q13 == "Véhicule motorisé (loué, emprunté, covoiturage)" ~ "Car",
    q13 == "Voiture personnelle" ~ "Car",
    q13 == " Ne s'applique pas" ~ "Other",
    q13 == "Ne sais pas" ~ "Other",
    q13 == "Scooter" ~ "Other",
    q13 == "Taxi" ~ "Other",
    q13 == "Transport en commun" ~ "Public Transportation",
    q13 == "Vélo en libre-service" ~ "Bicycle",
    q13 == "Vélo personnel" ~ "Bicycle"
  ))

table(ibiccs_clean$q13, ibiccs_clean$common_transportation)
```

# Recode Physically Active (Y/N)
```{r}

table(ibiccs_clean$q14)

ibiccs_clean <- ibiccs_clean %>%
  mutate(physically_active = case_when(
    q14 == "Ne sais pas/Ne s'applique pas" ~ "Other",
    q14 == "Refuse de répondre " ~ "Other",
    q14 == "Oui" ~ "Yes",
    q14 == "Non" ~ "No"
  ))

table(ibiccs_clean$q14, ibiccs_clean$physically_active)
```

# Recode Type of Physical Activity 
```
# Talk to Dr. Fuller about organizing questions 15 and 18
table(ibiccs_clean$q15)

table(ibiccs_clean$q18)

```
# Recode Days Per Week Spent Travelling via Car
```{r}

table(ibiccs_clean$q21)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_motor_vehicle = case_when(
    q21 == "0" ~ "0",
    q21 == "1" ~ "1",
    q21 == "2" ~ "2",
    q21 == "3" ~ "3",
    q21 == "4" ~ "4",
    q21 == "5" ~ "5",
    q21 == "6" ~ "6",
    q21 == "7" ~ "7",
    q21 == "98" ~ "NA",
    q21 == "99" ~ "NA"
  ))

table(ibiccs_clean$q21, ibiccs_clean$day_per_week_motor_vehicle)
```

# Recode Days Per Week Spent Travelling via Public Transport
```{r}

table(ibiccs_clean$q23)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_public_transit = case_when(
    q23 == "0" ~ "0",
    q23 == "1" ~ "1",
    q23 == "2" ~ "2",
    q23 == "3" ~ "3",
    q23 == "4" ~ "4",
    q23 == "5" ~ "5",
    q23 == "6" ~ "6",
    q23 == "7" ~ "7",
    q23 == "8" ~ "NA",
    q23 == "9" ~ "NA"
  ))

table(ibiccs_clean$q23, ibiccs_clean$day_per_week_public_transit)
```

# Recode Days Per Week Spent Travelling via Walking (Dr. Fuller)
```{r}

table(ibiccs_clean$q25)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_walking = case_when(
    q25 == "0" ~ "0",
    q25 == "1" ~ "1",
    q25 == "2" ~ "2",
    q25 == "3" ~ "3",
    q25 == "4" ~ "4",
    q25 == "5" ~ "5",
    q25 == "6" ~ "6",
    q25 == "7" ~ "7",
    q25 == "8" ~ "NA",
    q25 == "9" ~ "NA"
  ))

table(ibiccs_clean$q25, ibiccs_clean$day_per_week_walking)
```

# Recode Days Per Week Spent Travelling via Bike
```{r}

table(ibiccs_clean$q27)

ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_bike = case_when(
    q27 == "0" ~ "0",
    q27 == "1" ~ "1",
    q27 == "2" ~ "2",
    q27 == "3" ~ "3",
    q27 == "4" ~ "4",
    q27 == "5" ~ "5",
    q27 == "6" ~ "6",
    q27 == "7" ~ "7",
    q27 == "98" ~ "NA",
    q27 == "99" ~ "NA"
  ))

table(ibiccs_clean$q27, ibiccs_clean$day_per_week_bike)
```

# Recode Age
```{r}

table(ibiccs_clean$q42)
```

# Recode Marital Status
```{r}

table(ibiccs_clean$q44)

ibiccs_clean <- ibiccs_clean %>%
  mutate(marital_status = case_when(
    q44 == "Célibatiare" ~ "Single",
    q44 == "Divorcé(e)" ~ "Separated",
    q44 == "En couple" ~ "In a relationship",
    q44 == "Marié(e)/Conjoint de fait" ~ "In a relationship",
    q44 == "Refuse de répondre" ~ "NA",
    q44 == "Séparé(e)" ~ "Separated",
    q44 == "Veuf(ve)" ~ "Separated"
  ))

table(ibiccs_clean$q44, ibiccs_clean$marital_status)
```

# Recode Number of Children in Home
```{r}
table(ibiccs_clean$q45)

ibiccs_clean <- ibiccs_clean %>%
  mutate(children_household = case_when(
    q45 == "1" ~ "1",
    q45 == "2" ~ "2-3",
    q45 == "3" ~ "2-3",
    q45 == "4" ~ "4+",
    q45 == "5" ~ "4+",
    q45 == "6" ~ "4+",
    q45 == "7" ~ "4+",
    q45 == "8" ~ "0",
    q45 == "9" ~ "Refuse"
  ))

table(ibiccs_clean$q45, ibiccs_clean$children_household)
```

# Recode Months in Current Home?
```{r}
table(ibiccs_clean$q46b)
```

# Recode Ethnicity
```{r}
table(ibiccs_clean$q47)

ibiccs_clean <- ibiccs_clean %>%
  mutate(ethnicity = case_when(
    q47 == "Amérindien des États-Unis / Autochtone d'Amérique" ~ "Native American",
    q47 == "Arabe (Moyen-Orient, Afrique du Nord) " ~ "Other",
    q47 == "Asiatique / insulaire du Pacifique " ~ "Asian",
    q47 == "Autre " ~ "Other",
    q47 == "Blanc(che) / Caucasien " ~ "Causcasian",
    q47 == "Hispanique / Latino / Espagnol(e) " ~ "Hispanic",
    q47 == "Indien / Pakistanais" ~ "Other",
    q47 == "Je préfère ne pas répondre " ~ "Other",
    q47 == "Jewish " ~ "Refuse",
    q47 == "Mixed / Mixed race / Bi-racial" ~ "Other",
    q47 == "Noir(e) / Africain(e) / Afro-Américain(e)" ~ "African American"
  ))

table(ibiccs_clean$q47, ibiccs_clean$ethnicity)
>>>>>>> ae8da3969c80d352a583ccc0bac830e51a68508e
```

# Recode Type of Physical Activity 
```{r}
#Talk to Dr. Fuller about organizing questions 15 and 18
#Find IPAQ guidleines with Melissa
table(ibiccs_clean$q15)
summary(ibiccs_clean$q18)
```
# Recode Days Per Week Spent Travelling via Car
```{r}
table(ibiccs_clean$q21)
ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_motor_vehicle = case_when(
    q21 == "0" ~ "0",
    q21 == "1" ~ "1",
    q21 == "2" ~ "2",
    q21 == "3" ~ "3",
    q21 == "4" ~ "4",
    q21 == "5" ~ "5",
    q21 == "6" ~ "6",
    q21 == "7" ~ "7",
    q21 == "98" ~ "NA",
    q21 == "99" ~ "NA"
  ))
table(ibiccs_clean$q21, ibiccs_clean$day_per_week_motor_vehicle)
```

# Recode Days Per Week Spent Travelling via Public Transport
```{r}
table(ibiccs_clean$q23)
ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_public_transit = case_when(
    q23 == "0" ~ "0",
    q23 == "1" ~ "1",
    q23 == "2" ~ "2",
    q23 == "3" ~ "3",
    q23 == "4" ~ "4",
    q23 == "5" ~ "5",
    q23 == "6" ~ "6",
    q23 == "7" ~ "7",
    q23 == "8" ~ "NA",
    q23 == "9" ~ "NA"
  ))
table(ibiccs_clean$q23, ibiccs_clean$day_per_week_public_transit)
```

<<<<<<< HEAD
# Recode Days Per Week Spent Travelling via Walking
```{r}
table(ibiccs_clean$q25)
ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_walking = case_when(
    q25 == "0" ~ "0",
    q25 == "1" ~ "1",
    q25 == "2" ~ "2",
    q25 == "3" ~ "3",
    q25 == "4" ~ "4",
    q25 == "5" ~ "5",
    q25 == "6" ~ "6",
    q25 == "7" ~ "7",
    q25 == "8" ~ "NA",
    q25 == "9" ~ "NA"
  ))
table(ibiccs_clean$q25, ibiccs_clean$day_per_week_walking)
```

# Recode Days Per Week Spent Travelling via Bike
```{r}
table(ibiccs_clean$q27)
ibiccs_clean <- ibiccs_clean %>%
  mutate(day_per_week_bike = case_when(
    q27 == "0" ~ "0",
    q27 == "1" ~ "1",
    q27 == "2" ~ "2",
    q27 == "3" ~ "3",
    q27 == "4" ~ "4",
    q27 == "5" ~ "5",
    q27 == "6" ~ "6",
    q27 == "7" ~ "7",
    q27 == "98" ~ "NA",
    q27 == "99" ~ "NA"
  ))
table(ibiccs_clean$q27, ibiccs_clean$day_per_week_bike)
```

# Recode Age
```{r}
summary(ibiccs_clean$q42)
#CCHS/STATCAN or continuous
```

# Recode Marital Status
```{r}
table(ibiccs_clean$q44)
ibiccs_clean <- ibiccs_clean %>%
  mutate(marital_status = case_when(
    q44 == "Célibatiare" ~ "Single",
    q44 == "Divorcé(e)" ~ "Divorced/Separated/Widowed",
    q44 == "En couple" ~ "Relationship/Married/Common-Law",
    q44 == "Marié(e)/Conjoint de fait" ~ "Relationship/Married/Common-Law",
    q44 == "Refuse de répondre" ~ "NA",
    q44 == "Séparé(e)" ~ "Divorced/Separated/Widowed",
    q44 == "Veuf(ve)" ~ "Divorced/Separated/Widowed"
  ))
table(ibiccs_clean$q44, ibiccs_clean$marital_status)
```

# Recode Number of Children in Home
```{r}
table(ibiccs_clean$q45)
ibiccs_clean <- ibiccs_clean %>%
  mutate(children_household = case_when(
    q45 == "1" ~ "1",
    q45 == "2" ~ "2-3",
    q45 == "3" ~ "2-3",
    q45 == "4" ~ "4+",
    q45 == "5" ~ "4+",
    q45 == "6" ~ "4+",
    q45 == "7" ~ "4+",
    q45 == "8" ~ "0",
    q45 == "9" ~ "Refuse"
  ))
table(ibiccs_clean$q45, ibiccs_clean$children_household)
```

# Recode Months in Current Home?
```{r}
summary(ibiccs_clean$q46b)
```

# Recode Ethnicity
```{r}
table(ibiccs_clean$q47)
ibiccs_clean <- ibiccs_clean %>%
  mutate(ethnicity = case_when(
    q47 == "Amérindien des États-Unis / Autochtone d'Amérique" ~ "Native American",
    q47 == "Arabe (Moyen-Orient, Afrique du Nord) " ~ "Arab/Indian/Jewish/Mixed/Other",
    q47 == "Asiatique / insulaire du Pacifique " ~ "Asian",
    q47 == "Autre " ~ "Arab/Indian/Jewish/Mixed/Other",
    q47 == "Blanc(che) / Caucasien " ~ "Causcasian",
    q47 == "Hispanique / Latino / Espagnol(e) " ~ "Hispanic",
    q47 == "Indien / Pakistanais" ~ "Arab/Indian/Jewish/Mixed/Other",
    q47 == "Je préfère ne pas répondre " ~ "Refuse",
    q47 == "Jewish " ~ "Arab/Indian/Jewish/Mixed/Other",
    q47 == "Mixed / Mixed race / Bi-racial" ~ "Arab/Indian/Jewish/Mixed/Other",
    q47 == "Noir(e) / Africain(e) / Afro-Américain(e)" ~ "African American"
  ))
table(ibiccs_clean$q47, ibiccs_clean$ethnicity)
=======
Chicago <- filter(ibiccs_clean, ville == "Chicago")

Detroit <- filter(ibiccs_clean, ville == "Détroit")

NewYork <- filter(ibiccs_clean, ville == "New-York")

Philadelphia <- filter(ibiccs_clean, ville == "Philadelphie")

Montreal <- filter(ibiccs_clean, ville == "Montréal")

Toronto <- filter(ibiccs_clean, ville == "Toronto")

Vancouver <- filter(ibiccs_clean, ville == "Vancouver")
>>>>>>> ae8da3969c80d352a583ccc0bac830e51a68508e
```

# Recode Country Born
```{r}
table(ibiccs_clean$q48)
ibiccs_clean <- ibiccs_clean %>%
  mutate(country_born = case_when(
    q48 == 1 ~ "Canada",
    q48 == 2 ~ "United States",
    q48 >= 3 | q48 <=81 ~ "Other", 
    TRUE ~ "Not stated"
  ))
table(ibiccs_clean$q48, ibiccs_clean$country_born)
```

# Recode Motor Vehicle Access
```{r}
<<<<<<< HEAD
table(ibiccs_clean$q50)

ibiccs_clean <- ibiccs_clean %>%
  mutate(motor_vehicle_access = case_when(
    q50 == "Ne sais pas/Ne s'applique pas" ~ "NA",
    q50 == "Non" ~ "No",
    q50 == "Oui" ~ "Yes"
  ))
table(ibiccs_clean$q50, ibiccs_clean$motor_vehicle_access)
```

# Recode Education Level
```{r}
table(ibiccs_clean$q51)
ibiccs_clean <- ibiccs_clean %>%
  mutate(education = case_when(
    q51 == "Aucun grade, certificat ou diplôme" ~ "Other",
    q51 == "Autre (précisez)" ~ "Other",
    q51 == "Baccalauréat" ~ "Baccalaureate",
    q51 == "Cégep" ~ "Cégep",
    q51 == "Certificat d'école de métier, certificat ou diplôme" ~ "Certificate/Diploma",
    q51 == "Diplôme d'études secondaire ou l'équivalent" ~ "High School/Lower",
    q51 == "Diplôme universitaire supérieur au baccalauréat" ~ "Graduate School",
    q51 == "École primaire" ~ "High School/Lower",
    q51 == "Refuse de répondre" ~ "Other"
  ))
table(ibiccs_clean$q51, ibiccs_clean$education)
```

# Recode Occupation Status
```{r}
table(ibiccs_clean$Q52_occupational_status_category)
ibiccs_clean <- ibiccs_clean %>%
  mutate(occupation_status = case_when(
    Q52_occupational_status_category == "Disability" ~ "Unemployed",
    Q52_occupational_status_category == "Full time or Self-employed" ~ "Employed",
    Q52_occupational_status_category == "Homemaker or parental leave" ~ "Unemployed",
    Q52_occupational_status_category == "Part time" ~ "Employed",
    Q52_occupational_status_category == "Retired" ~ "Unemployed",
    Q52_occupational_status_category == "Student" ~ "Student",
    Q52_occupational_status_category == "Unemployed seeking work" ~ "Unemployed"
  ))
table(ibiccs_clean$Q52_occupational_status_category, ibiccs_clean$occupation_status)
```

# Recode Household Income
```{r}
table(ibiccs_clean$q53)
ibiccs_clean <- ibiccs_clean %>%
  mutate(household_income = case_when(
    q53 == "Moins de 10000 $ par année" ~ "$0-$19999",
    q53 == "Entre 10000 $ and 19999 $ par année" ~ "$0-$19999",
    q53 == "Entre 20000 $ and 34999 $ par année" ~ "$20000-$49999",
    q53 == "Entre 35000 $ and 49999 $ par année" ~ "$20000-$49999",
    q53 == "Entre 50000 $ and 74999 $ par année" ~ "$50000-$74999",
    q53 == "Entre 75000 $ and 99999 $ par année" ~ "$75000-$99999",
    q53 == "Entre 100000 $ and 149999 $ par année" ~ "$100000-149999",
    q53 == "Entre 150000 $ and 199999 $ par année" ~ "$150000+",
    q53 == "Plus de 200000 $ par année" ~ "$150000+",
    q53 == "Refuse de répondre" ~ "Refuse"
  ))
table(ibiccs_clean$q53, ibiccs_clean$household_income)
```

# Filtering Out Cities
```{r}
Boston <- filter(ibiccs_clean, ville == "Boston")

Chicago <- filter(ibiccs_clean, ville == "Chicago")

Detroit <- filter(ibiccs_clean, ville == "Détroit")

NewYork <- filter(ibiccs_clean, ville == "New-York")

Philadelphia <- filter(ibiccs_clean, ville == "Philadelphie")

Montreal <- filter(ibiccs_clean, ville == "Montréal")
=======
ibiccs <- select(ibiccs_clean, lang, q54, ville, q2, q13, q14, q15, q18, q21, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)
 
### Add the prepost variable

Boston <- filter(ibiccs_clean, ville == "Boston")


Boston1 <- select(Boston, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Chicago1 <- select(Chicago, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Detroit1 <- select(Detroit, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

NewYork1 <- select(NewYork, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Philadelphia1 <- select(Philadelphia, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Montreal1 <- select(Montreal, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Toronto1 <- select(Toronto, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)

Vancouver1 <- select(Vancouver, lang, q54, ville, q2, q13, q14, q15, q18, q21, q22b, q22c, q22d, q22e, q22f_m1, q23, q25, q27, q42, q44, q45, q46b, q47, q48, q49, q50, q51, Q52_occupational_status_category, q53, bmi, bmi_category, WalkScore, WalkScoreLabel, TransitScore, TransitScoreLabel, BikeScore, BikeScoreLabel, DiningandDrinkingScore, GroceryScore)
>>>>>>> ae8da3969c80d352a583ccc0bac830e51a68508e

Toronto <- filter(ibiccs_clean, ville == "Toronto")

Vancouver <- filter(ibiccs_clean, ville == "Vancouver")
```


# Filtering Out Variables in USA Data
```{r}
vars_clean <- c('language', 'ville', 'gender', 'health', 'common_transportation', 'physically_active', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'q42', 'marital_status', 'children_household', 'ethnicity', 'q48', 'motor_vehicle_access', 'education', 'occupation_status', 'household_income', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')

ibiccs <- select(ibiccs_clean, vars_clean)
Boston <- select(Boston, vars_clean)
Chicago <- select(Chicago, vars_clean)
Detroit <- select(Detroit, vars_clean)
NewYork <- select(NewYork, vars_clean)
Philadelphia <- select(Philadelphia, vars_clean)
Montreal <- select(Montreal, vars_clean)
Toronto <- select(Toronto, vars_clean)
Vancouver <- select(Vancouver, vars_clean)
city <- rbind(Philadelphia, NewYork, Detroit, Chicago, Boston, Montreal, Toronto, Vancouver)
```

# Binding by Country
```{r}
city_USA <- rbind(Philadelphia, NewYork, Detroit, Chicago, Boston)
city_CAN <- rbind(Montreal, Toronto, Vancouver)
```


#Tables for Each City and Combined
```{r}
<<<<<<< HEAD
vars <- c('language', 'ville', 'gender', 'health', 'common_transportation', 'physically_active', 'day_per_week_motor_vehicle', 'day_per_week_public_transit', 'day_per_week_walking', 'day_per_week_bike', 'q42', 'marital_status', 'children_household', 'ethnicity', 'q48', 'motor_vehicle_access', 'education', 'occupation_status', 'household_income', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')
CreateTableOne(vars = vars, data = Boston)
CreateTableOne(vars = vars, data = Chicago)
CreateTableOne(vars = vars, data = Detroit)
CreateTableOne(vars = vars, data = NewYork)
CreateTableOne(vars = vars, data = Philadelphia)
CreateTableOne(vars = vars, data = Montreal)
CreateTableOne(vars = vars, data = Toronto)
CreateTableOne(vars = vars, data = Vancouver)
=======
vars <- c('lang', 'q54', 'ville', 'q2', 'q13', 'q14', 'q15', 'q18', 'q21', 'q22b', 'q22c', 'q22d', 'q22e', 'q22f_m1', 'q23', 'q25', 'q27', 'q42', 'q44', 'q45', 'q46b', 'q47', 'q48', 'q49', 'q50', 'q51', 'Q52_occupational_status_category', 'q53', 'bmi', 'bmi_category', 'WalkScore', 'WalkScoreLabel', 'TransitScore', 'TransitScoreLabel', 'BikeScore', 'BikeScoreLabel', 'DiningandDrinkingScore', 'GroceryScore')
CreateTableOne(vars = vars, data = Boston1)
CreateTableOne(vars = vars, data = Chicago1)
CreateTableOne(vars = vars, data = Detroit1)
CreateTableOne(vars = vars, data = NewYork1)
CreateTableOne(vars = vars, data = Philadelphia1)
CreateTableOne(vars = vars, data = Montreal1)
CreateTableOne(vars = vars, data = Toronto1)
CreateTableOne(vars = vars, data = Vancouver1)
>>>>>>> ae8da3969c80d352a583ccc0bac830e51a68508e
CreateTableOne(vars = vars, data = city, includeNA = TRUE)
```

# Fix this Code - Breaks Session
table1 <- ibiccs %>%
            group_by(ville) %>%
              CreateTableOne(vars = vars, data = ibiccs)


lang_lm <- lm(bmi ~ cbind(lang, q2), Boston1)
tidy(lang_lm)

# Histogram of BMI
```{r}
hist_bmi <- ggplot(city, aes(bmi)) + 
  geom_histogram()
plot(hist_bmi)

hist_bmi_city <- ggplot(city, aes(bmi)) + 
  geom_density(aes(group = ville, colour = ville)) +
  theme_minimal()
plot(hist_bmi_city)
```

To do:
2. Linear Regressions (loop)

### Linear regression




## Junk Code
```
lm1 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + TransitScore + GroceryScore + factor(ville), data = ibiccs)
summary(lm1)
confint(lm1)

lm2 <- lm(bmi ~ WalkScore + DiningandDrinkingScore + + TransitScore + GroceryScore + factor(ville) + lang + q44 + q47 + q51 + Q52_occupational_status_category + q54, data = ibiccs)
summary(lm2)
confint(lm2)
```

```
usda_zip <- dplyr::full_join(USDA, USA_ZIP, by = "CensusTract")

usda_zip_food <- usda_zip %>%
                    group_by(zip) %>%
                        summarize(
                          food = mean(foodvariable)
                        )
```

```
library(plyr)
city$zip <- as.numeric(city$RTA_zip)
USA_ZIP$CensusTract <- as.numeric(USA_ZIP$tract)
```

```
library(plyr)
city$CensusTract <- as.numeric(city$zip)
```


```
city_zip <- dplyr::left_join(city, usda_zip, by = "zip")
table(city_zip$ville)

summary(city$WalkScore)
summary(city$DiningandDrinkingScore)
summary(city$GroceryScore)
summary(city$TransitScore)
```

